My title

### 2024-09-20 paper/paper.qmd
change paper

```{r}
#| label: fig-clean-tfs
#| fig-cap: TFS response time and estimated dollar loss over time
#| echo: false
#| fig-subcap: ["TFS response time over time","Estimated dollar loss over time"]
#| layout-ncol: 2

@@

cleaned_data_tfs |>
  ggplot(mapping = aes(x = tfs_alarm_time, y = estimated_dollar_loss)) + 
  geom_line() +
  theme_minimal() +
  labs(
    x = "Alarm Time", y = "Estimated dollar loss",
  )
```

>>>>

@fig-clean-tfs-diff-dollar-time-1 shows the line plot of Toronto Fire Service's response time over the period between 2013 to 2023.

```{r}
#| label: fig-clean-tfs-diff-dollar-time
#| fig-cap: TFS response time and estimated dollar loss over time
#| echo: false
#| fig-subcap: ["TFS response time over time","Estimated dollar loss over time"]
#| layout-ncol: 2

@@

cleaned_data_tfs |>
  ggplot(mapping = aes(x = tfs_alarm_time, y = estimated_dollar_loss)) + 
  geom_line() +
  theme_minimal() +
  labs(
    x = "Alarm Time", y = "Estimated dollar loss",
  )

```

```{r}
#| label: fig-clean-tfs-boxplot
#| fig-cap: "Boxplot of TFS response time data and estimated dollar loss"
#| fig-subcap: ["Boxplot of TFS response time", "Boxplot of estimated dollar loss"]
#| echo: false
#| layout-ncol: 2

cleaned_data_tfs |>
  ggplot(aes(x = "", y = time_diff)) +
  geom_boxplot() +
  labs(y = "TFS response time", x = "") + 
  theme_classic()

cleaned_data_tfs |>
  ggplot(aes(x = "", y = estimated_dollar_loss)) +
  geom_boxplot() +
  labs(y = "Estimated dollar loss", x = "") + 
  theme_classic()

```

```{r}
#| label: tbl-clean-tfs-summary
#| tbl-cap: "Summary Statistic of TFS response time data and estimated dollar loss"
#| tbl-subcap: ["Summary of TFS response time", "Summary of estimated dollar loss"]
#| echo: false
#| layout-ncol: 2

summary_response_time <- 
  cleaned_data_tfs$time_diff |>
  summary() |> append(sd(cleaned_data_tfs$time_diff))

summary_response_time <- data.frame(
  Statistic = c(names(summary(cleaned_data_tfs$time_diff)), "SD"),
  Value = as.vector(summary_response_time)
)

kable(summary_response_time, col.names = c("Statistic", "Value"))

summary_dollar_loss <- 
  cleaned_data_tfs$estimated_dollar_loss |>
  summary() |> append(sd(cleaned_data_tfs$estimated_dollar_loss))

summary_dollar_loss <- data.frame(
  Statistic = c(names(summary(cleaned_data_tfs$estimated_dollar_loss)), "SD"),
  Value = as.vector(summary_dollar_loss)
)

kable(summary_dollar_loss, col.names = c("Statistic", "Value"))

```
